---
title: "landfileRclient quick start guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{landfileRclient quick start guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a quick start guide for the landfilesRclient package. This package provides functions to connect with your password and id to the LandFiles API, and then import data from LandFiles directly to R through the API.

# Setup 

```{r setup}
library(landfilesRclient)
```

# Functions

All functions in the landfilesRclient send request to the landfiles API, and print a message ine the R console according to  the status of the request:

- 200 : means the request has succeeded
- 300 : means the request was reoriented elsewhere
- 400 : means the request failed from your side (your fault)
- 500 : means that the request failed from the server (not your fault)

If the status is not 200, the function stops.

## function getToken
The function getToken() send a request to the landfiles API in order to retrieve a token. This function needs 3 arguments:

- url : a string url of the API, by default set to "https://api.landfiles.fr/api/authenticationservice/auth/oauth/token"
- username : a string with your username provided by Landfiles
- password : a string with your password provided by Landfiles

```{r getToken example}
#not run  getToken(username = "",password = "")

```

If the connection is successful, this give you a token that could be reused to query data from the landfiles API. 

## function getGroups
The function getGroups() send a request to the landfiles API in order to get back all groups available with the token submitted, according to the access permission of the user in Landfiles.
This function has only one argument, the token :

- token :  a string with the token from getToken function

```{r getGroups example}
#not run getGroups(token=token) 
```

The function return a data frame with the id, name and url of each group.

## function getFarms
The function getFarms() send a request to the landfiles API in order to get back all farms registered in a given group.
This function has two arguments  :

- token :  a string with the token from getToken function
- group : the id of the group, for instance "GR-96c6c34e-e884-483e-94af-6fabc055c4bd"

```{r getFarms example}
#not run farms <- getFarms(group = "GR-96c6c34e-e884-483e-94af-6fabc055c4bd",
#                  token = token)
```

The function return a data frame with the id, name and url, description, town, postalCode, country and coordinates (latitude,longitude WGS84) of each farm.

## function getPlots
The function getPlots() send a request to the landfiles API in order to get back all plots registered in a given group.
This function has two arguments  :

- token :  a string with the token from getToken function
- group : the id of the group, for instance "GR-96c6c34e-e884-483e-94af-6fabc055c4bd"

```{r getPlots}
#not run plots <- getPlots(group = "GR-96c6c34e-e884-483e-94af-6fabc055c4bd",
#        token = token)
```

The function return a data frame with the id (uuid), metadata and coordinates (latitude and longitude WGS84) of each plot.

## function getObs
The function getObs() send a request to the landfiles API in order to get back all plots registered in a given group.
This function has two arguments  :

- token :  a string with the token from getToken function
- group : the id of the group, for instance "GR-96c6c34e-e884-483e-94af-6fabc055c4bd"
- startDate : a string with the start date of observations in format YYYY-MM-DD, by default "2022-01-01"
- endDate : a string with the end date of observations in format YYYY-MM-DD, by default "2022-12-31"

```{r getObs}
#not run obs <- getObs(group = "GR-96c6c34e-e884-483e-94af-6fabc055c4bd",
#              token = token)
```

The function return a list with two elements :

- a data frame with the observations 
- a vector of the names of columns of the data frame.

