---
title: "landfileRclient quick start guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{comment-utiliser-mon-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(landfilesRclient)
```

# Functions
## getToken
The function getToken() send a request to the landfiles API in order to retrieve a token. This function needs 3 arguments:

- url : the url of the API, by default set to "https://api.landfiles.fr/api/authenticationservice/auth/oauth/token"
- username : your username
- password : your password

```{r getToken example}
#not run  getToken(username = "",password = "")

```

If the connection is successful, this give you a token that could be reused to query data from the landfiles APIP. The function also print a message according to  the status of the request:

- 200 and family: means the request has succeeded
- 300 and family: means the request was reoriented elsewhere
- 400 and family: means the request failed from your side (your fault)
- 500 and family: means that the request failed from the server (not your fault)
